Proportional multi-state multiple-cohort life table model

### 2018-04-18 MSLT/MSLTdoc.Rmd
Replaces spline for splinefunc
The spline function is best to use here, as before I was not interpolating within ages.

6) Create age categories index in GBDdata (upper limit age group to match injury data), total of 20 age groups. These are the age cohorts to simulate. 
```{r, echo=TRUE}
GBDdata$age_cat [GBDdata$age =="under 5"] <- 2
GBDdata$age_cat [GBDdata$age =="5 to 9"] <- 7
GBDdata$age_cat [GBDdata$age =="10 to 14"] <- 12
GBDdata$age_cat [GBDdata$age =="15 to 19"] <- 17
GBDdata$age_cat [GBDdata$age =="20 to 24"] <- 22
GBDdata$age_cat [GBDdata$age =="25 to 29"] <- 27
GBDdata$age_cat [GBDdata$age =="30 to 34"] <- 32
GBDdata$age_cat [GBDdata$age =="35 to 39"] <- 37
GBDdata$age_cat [GBDdata$age =="40 to 44"] <- 42
GBDdata$age_cat [GBDdata$age =="45 to 49"] <- 47
GBDdata$age_cat [GBDdata$age =="50 to 54"] <- 52
GBDdata$age_cat [GBDdata$age =="55 to 59"] <- 57
GBDdata$age_cat [GBDdata$age =="60 to 64"] <- 62
GBDdata$age_cat [GBDdata$age =="65 to 69"] <- 67
GBDdata$age_cat [GBDdata$age =="70 to 74"] <- 72
GBDdata$age_cat [GBDdata$age =="75 to 79"] <- 77
GBDdata$age_cat [GBDdata$age =="80 to 84"] <- 82
GBDdata$age_cat [GBDdata$age =="85 to 89"] <- 87
GBDdata$age_cat [GBDdata$age =="90 to 94"] <- 92
GBDdata$age_cat [GBDdata$age =="95 plus"] <- 97
```

@@

data <- filter(GBDGL, measure == "ylds (years lived with disability)", sex == "female", cause == "all causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate)

x=data$age_cat
y=log(data$one_rate)

interpolated<- as.data.frame(spline(x, y, n = 5 *length (x), xmin = min(x-2), xmax = max(x + 2)))
interpolated$y <- exp(y)
plot(x,y)

@@

    #print(paste(sex, measure, "interpolated_data", sep = "_"))
    #print(paste(sex, measure, "interpolated", sep = "_"))

@@

interpolated <- as.data.frame(spline(x, y, n = 5 *length (x), xmin = min(x-2), xmax = max(x + 2)))
interpolated$y <- exp(y)
assign(paste(sex, measure, "interpolated", sep = "_"), interpolated)
plot(x,y)

@@

plot(male_deaths_interpolated_data$age_cat, male_deaths_interpolated_data$one_rate)

plot(female_deaths_interpolated$x, female_deaths_interpolated$y)

>>>>

6) Create age categories index in GBDdata (upper limit age group to match injury data), total of 20 age groups. These are the age cohorts to simulate. 
```{r, echo=TRUE}
GBDdata$age_cat [GBDdata$age =="under 5"] <- 5
GBDdata$age_cat [GBDdata$age =="5 to 9"] <- 10
GBDdata$age_cat [GBDdata$age =="10 to 14"] <- 15
GBDdata$age_cat [GBDdata$age =="15 to 19"] <- 20
GBDdata$age_cat [GBDdata$age =="20 to 24"] <- 25
GBDdata$age_cat [GBDdata$age =="25 to 29"] <- 30
GBDdata$age_cat [GBDdata$age =="30 to 34"] <- 35
GBDdata$age_cat [GBDdata$age =="35 to 39"] <- 40
GBDdata$age_cat [GBDdata$age =="40 to 44"] <- 45
GBDdata$age_cat [GBDdata$age =="45 to 49"] <- 50
GBDdata$age_cat [GBDdata$age =="50 to 54"] <- 55
GBDdata$age_cat [GBDdata$age =="55 to 59"] <- 60
GBDdata$age_cat [GBDdata$age =="60 to 64"] <- 65
GBDdata$age_cat [GBDdata$age =="65 to 69"] <- 70
GBDdata$age_cat [GBDdata$age =="70 to 74"] <- 75
GBDdata$age_cat [GBDdata$age =="75 to 79"] <- 80
GBDdata$age_cat [GBDdata$age =="80 to 84"] <- 85
GBDdata$age_cat [GBDdata$age =="85 to 89"] <- 90
GBDdata$age_cat [GBDdata$age =="90 to 94"] <- 95
GBDdata$age_cat [GBDdata$age =="95 plus"] <- 100
```

@@

@@

@@

interpolation_func <- splinefun(x, y, method = "natural", ties = mean)

interpolated <- as.data.frame(interpolation_func(seq(0, 99, 1)))
ages <- seq(0,99,by=1)
interpolated <- cbind(interpolated, ages)
interpolated[,1] <- exp(interpolated[,1])
colnames(interpolated)[1] <- "rate"

assign(paste(sex, measure, "interpolated", sep = "_"), interpolated)
plot(interpolated$age,interpolated$rate)

@@
